---
title: "Homework 6 solutions"
author: "Rio Yan"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(ggcorrplot)
set.seed(1)

knitr::opts_chunk$set(
  fig.width = 9,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa,AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r, echo=FALSE}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore,MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digit = 3)
```


Try this across cities.

```{r}
models_results_df =
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex,
    data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
models_results_df %>% 
  filter(term == "victim_raceWhite") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

__Comment__: 
We can see that Tampa, FL has the lowest OR with small 95% CI range and Boston,MA has the highest and has the largest 95% CI range. All the OR are above 0, meaning that comparing to black population, when victim is white, the cases have a higher chance of being solved. 



## Problem 2

Find some residuals

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex), #convert numeric to factor
    frace = factor(frace), #convert numeric to factor
    malform = factor(malform), #convert numeric to factor
    mrace = factor(mrace) #convert numeric to factor
  ) 

baby_df %>% 
  anyNA()
#check if there is NA: no NAs
```


```{r}
model.matrix(~0+., data=baby_df) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  ggcorrplot(show.diag = F, type="lower", 
             lab=TRUE, lab_size=2, 
             title = "Correlation of parameters of interest")
```

Using correlation matrix to identify which parameters have higher positive association with birth weight. Decide to pick delwt(mother’s weight at delivery (pounds)) and gaweeks(gestational age in weeks). 

fit a model

```{r}
model_fit = lm(bwt ~ delwt + gaweeks, data = baby_df)

#See quality of the model 
model_fit %>%
  broom::glance()

#Both are significant coeff
model_fit %>%
  broom::tidy()
```


plot residual

```{r}
baby_df %>%
  modelr::add_residuals(model_fit) %>%
  ggplot(aes(x = resid)) + geom_density()
```

```{r}
baby_df %>% 
  modelr::add_residuals(model_fit) %>% 
  modelr::add_predictions(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(
    title = "Residuals against fitted value",
    x = "Fitted value",
    y = "Residuals"
  )
```

Overall, residuals are centered around 0. 


compare models
```{r}
model_fit = lm(bwt ~ delwt + gaweeks, data = baby_df)
model_1 = lm(bwt ~ blength + gaweeks, data = baby_df)
model_2 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
```



```{r}
cv_df =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    model_fit = map(train, ~lm(bwt ~ delwt + gaweeks, data = .x)),
    model_1 = map(train, ~lm(bwt ~blength + gaweeks, data = .x)),
    model_2 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_fit = map2_dbl(model_fit, test, ~rmse(model = .x, data = .y)),
    rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))
  )
```

plot prediction error for each models

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()

##change name
```

From the graph we can see that model 2 using head circumference, length, sex, and all interactions has the lower rmse, meaning a better model, while the model I created has the highest rmse. This may be because adding too many variable increases the degrees of value and increases it's predictive accuracy. 


## Problem 3

import data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(tmax, tmin)
```


Bootstrapping

For $\hat{r^2}$

```{r}
r_sq = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(results) 

#distribution
r_sq %>% 
  ggplot(aes(x = r.squared)) + geom_density() +
  labs(
    title = "Distribution of R Squared Values"
  )


#95% CI
r2_ci_lower = quantile(pull(r_sq, r.squared), 0.025)
r2_ci_upper = quantile(pull(r_sq, r.squared), 0.975)
```


For $log(\hat{\beta_0} * \hat{\beta_1})$

```{r}
betas = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  mutate(
    term = str_replace(term,"\\(Intercept\\)","beta0"),
    term = str_replace(term,"tmin","beta1")
  ) %>% 
  spread(term, estimate) %>%
  group_by(.id) %>%
  summarise_all(na.omit) %>% 
  mutate(
    beta_c = log(beta0 * beta1)
  ) 


  toDelete = seq(1, nrow(betas), 2)
betas = betas[ toDelete ,]
  
  
#distribution
betas %>% 
  ggplot(aes(x = beta_c)) + geom_density() +
  labs(
    title = "Distribution of Log Estimates"
  )

#95% CI
beta_ci_lower = quantile(pull(betas,beta_c), 0.025)
beta_ci_upper = quantile(pull(betas,beta_c), 0.975)
```


The distributions of $\hat{r^2}$ and $log(\hat{\beta_0} * \hat{\beta_1})$ using bootstrap seem to be following a normal distribution with rsquare's distribution centered around 0.915 and beta centered around 2.02. Both are slightly left skewed. $\hat{r^2}$ 95%CI is (`r r2_ci_lower`, `r r2_ci_upper`) and $log(\hat{\beta_0} * \hat{\beta_1})$ 95%CI is (`r beta_ci_lower`, `r beta_ci_upper`). 